---
title: "learnTidy"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
learnr::tutorial_options(exercise.completion = FALSE)
```

## Files

------

### Names

`r emo::ji('pushpin')` Rules :

- File names should be meaningful and end in .R. 
- Avoid using special characters in file names - stick with numbers, letters, `-`, and `_`. 

```{r q-files-1-setup}
`fit_models.R` <- "Correct"
`utility_functions.R` <- "Correct"
`fit models.R` <- "Wrong"
`utility functions.r` <- "Wrong"
```

<p font-size:2em> Exercise : </p>
Fix following Names and run it with `Run code`. 
If it is correct, `Correct` will be returned.

```{r q-files-1, exercise = TRUE, exercise.setup = "q-files-1-setup"}
`fit models.R`
`utility functions.r`
```

`r emo::ji('pushpin')` Rules :

- If files should be run in a particular order, prefix them with numbers. 
- If it seems likely you’ll have more than 10 files, left pad with zero:

```
00_download.R
1_explore.R
02_trim.R
...

09_model.R
visualize.R
11_summary.R

```

```{r q-files-2-setup}
`01_explore.R` <- "Correct"
`10_visualize.R` <- "Correct"

`1_explore.R` <- "Wrong"
`visualize.R` <- "Wrong"
```

<p font-size:2em> Exercise : </p>
Fix following name of codes, `1_explore.R` and `visualize.R` then run it with `Run code`. 
If it is correct, `TRUE` will be returned.

```{r q-files-2, exercise = TRUE, exersie.setup = "q2-setup"}
`1_explore.R`
`visualize.R`
```

------

### Internal Structure

`r emo::ji('pushpin')` Rules :

- Use commented lines of `-` and `=` to break up your file into easily readable chunks.

<p font-size:2em> Question : </p>
```{r q-files-3, echo = FALSE}
question("Select all recommended style of comment.",
  answer("#　Comment style A", correct = FALSE),
  answer("#　Comment style B -----------------------", correct = TRUE),
  answer("#Comment style C ========", correct = FALSE),
  answer("#　Comment style D ========", correct = TRUE),
  allow_retry = TRUE,
  random_answer_order = TRUE
)
```


## Syntax

------

### Object Names

`r emo::ji('pushpin')` Rules :

- Variable and function names should use only lowercase letters, numbers, and `_`. 
- Use underscores (`_`) (so called snake case) to separate words within a name.

```{r q-syntax-1-setup}
`day_one` <- "Correct"
`DayOne` <- "Wrong"
```

<p font-size:2em> Exercise : </p>
Fix following codes and run it with `Run code`. 
If it is correct, `Correct` will be returned.

```{r q-syntax-1, exercise = TRUE, exercise.setup = "q-syntax-1-setup"}
`DayOne` 
```

`r emo::ji('pushpin')` Rules :

- Base R uses dots in function names (`contrib.url()`) and class names (`data.frame`), but it’s better to reserve dots exclusively for the S3 object system. In S3, methods are given the name function.class. 
- If you also use . in function and class names, you end up with confusing methods like as.data.frame.data.frame().
- Generally, variable names should be nouns and function names should be verbs. Strive for names that are concise and meaningful (this is not easy!).
- Where possible, avoid re-using names of common functions and variables. This will cause confusion for the readers of your code.

<p font-size:2em> Question : </p>
```{r q-syntax-2, echo = FALSE}
question("Select all recommended style of object name.",
  answer("first_day_of_the_month", correct = FALSE),
  answer("djm1", correct = FALSE),
  answer("dayone", correct = FALSE),
  answer("T", correct = FALSE),
  answer("t", correct = FALSE),
  answer("c", correct = FALSE),
  answer("C", correct = TRUE),
  answer("mean", correct = TRUE),
  allow_retry = TRUE,
  random_answer_order = TRUE
)
```

------

### Spacing

#### Commas

`r emo::ji('pushpin')` Rules :

- Always put a space after a comma, never before, just like in regular English. 

```{r q-syntax-3-setup}
`x[, 1]` <- "Correct"
`x[,1]` <- "Wrong"
`x[ , 1]` <- "Wrong"
`x[ ,1]` <- "Wrong"
```

<p font-size:2em> Exercise : </p>
Fix following codes and run it with `Run code`. 
If it is correct, `Correct` will be returned.

```{r q-syntax-3, exercise = TRUE, exercise.setup = "q-syntax-3-setup"}
`x[,1]` 
```

#### Parentheses

`r emo::ji('pushpin')` Rules :

- Do not put spaces inside or outside parentheses for regular function calls.
- Place a space before and after `()` when used with `if`, `for`, or `while`.
- Place a space after `()` used for function arguments.

```{r q-syntax-4-setup}
`mean(x, na.rm = TRUE)` <- "Correct"
`mean (x, na.rm = TRUE)` <- "Wrong"
`mean( x, na.rm = TRUE )` <- "Wrong"
`mean( x, na.rm = TRUE ) ` <- "Wrong"
`mean ( x, na.rm = TRUE ) ` <- "Wrong"

`if(debug) show(x)` <- "Wrong"
`if (debug) show(x)` <- "Correct"

```

<p font-size:2em> Exercise : </p>
Fix following codes and run it with `Run code`. 
If it is correct, `Correct` will be returned.

```{r q-syntax-4, exercise = TRUE, exercise.setup = "q-syntax-4-setup"}
`mean ( x, na.rm = TRUE ) ` 
`if(debug) show(x)`
```

#### Infix operators

`r emo::ji('pushpin')` Rules :

- Most infix operators (`==`, `+`, `-`, `<-`, etc.) should always be surrounded by spaces:

```{r q-syntax-5-setup}
`height <- (feet * 12) + inches` <- "Correct"
`mean(x, na.rm = TRUE)` <- "Correct"
`height<-feet*12+inches` <- "Wrong"
`mean(x, na.rm=TRUE)` <- "Wrong"
```

<p font-size:2em> Exercise : </p>
Fix following codes and run it with `Run code`. 
If it is correct, `Correct` will be returned.

```{r q-syntax-5, exercise = TRUE, exercise.setup = "q-syntax-5-setup"}
`mean ( x, na.rm = TRUE ) ` 
`if(debug) show(x)`
```

`r emo::ji('pushpin')` Rules :

- There are a few exceptions, which should never be surrounded by spaces:
- The operators with high precedence: `::`, `:::`, `$`, `@`, `[`, `[[`, `^`, unary `-`, unary `+`, and `:`.

```{r q-syntax-6-setup}
`sqrt(x^2 + y^2)` <- "Correct"
`df$z` <- "Correct"
`x <- 1:10` <- "Correct"
`sqrt(x ^ 2 + y ^ 2)` <- "Wrong"
`df $ z` <- "Wrong"
`x <- 1 : 10` <- "Wrong"
```

<p font-size:2em> Exercise : </p>
Fix following codes and run it with `Run code`. 
If it is correct, `Correct` will be returned.

```{r q-syntax-6, exercise = TRUE, exercise.setup = "q-syntax-6-setup"}
`sqrt(x ^ 2 + y ^ 2)` 
`df $ z`
`x <- 1 : 10`
```

`r emo::ji('pushpin')` Rules :

- Single-sided formulas (`~`) when the right-hand side is a single identifier:
- Note that single-sided formulas with a complex right-hand side do need a space:

```{r q-syntax-7-setup}
`~foo` <- "Correct"
`tribble(~col1, ~col2, "a", "b")` <- "Correct"
`~ .x + .y` <- "Correct"
`~ foo` <- "Wrong"
`tribble(~ col1, ~ col2, "a", "b")` <- "Wrong"
`~.x + .y` <- "Wrong"
```

<p font-size:2em> Exercise : </p>
Fix following codes and run it with `Run code`. 
If it is correct, `Correct` will be returned.

```{r q-syntax-7, exercise = TRUE, exercise.setup = "q-syntax-7-setup"}
`~ foo`
`tribble(~ col1, ~ col2, "a", "b")`
`~.x + .y`
```

`r emo::ji('pushpin')` Rules :

- When used in tidy evaluation `!!` (bang-bang) and `!!!` (bang-bang-bang) (because have precedence equivalent to unary `-`/`+`)

```{r q-syntax-8-setup}
`call(!!xyz)` <- "Correct"
`tribble(~col1, ~col2, "a", "b")` <- "Correct"
`~ .x + .y` <- "Correct"
`call(!! xyz)` <- "Wrong"
`call( !! xyz)` <- "Wrong"
`call(! !xyz)` <- "Wrong"
```

<p font-size:2em> Exercise : </p>
Fix following codes and run it with `Run code`. 
If it is correct, `Correct` will be returned.

```{r q-syntax-8, exercise = TRUE, exercise.setup = "q-syntax-8-setup"}
`call(!! xyz)`
`call( !! xyz)`
`call(! !xyz)`
```

`r emo::ji('pushpin')` Rules :

- The help (`?`) operator.

```{r q-syntax-9-setup}
`package?stats` <- "Correct"
`?mean` <- "Correct"
`package ? stats` <- "Wrong"
`? mean` <- "Wrong"
```

<p font-size:2em> Exercise : </p>
Fix following codes and run it with `Run code`. 
If it is correct, `Correct` will be returned.

```{r q-syntax-9, exercise = TRUE, exercise.setup = "q-syntax-9-setup"}
`package ? stats`
`? mean`
```

#### Extra spaces

`r emo::ji('pushpin')` Rules :

- Adding extra spaces ok if it improves alignment of `=` or `<-`.

```R 
# Good
list(
  total = a + b + c,
  mean = (a + b + c) / n
)

# Also fine
list(
  total = a + b + c,
  mean  = (a + b + c) / n
)
```

------

### Argument Names

`r emo::ji('pushpin')` Rules : 

- A function’s arguments typically fall into two broad categories: 
- one supplies the **data** to compute on; 
- the other controls the **details** of computation. 
- When you call a function, you typically omit the names of data arguments, because they are used so commonly. 
- If you override the default value of an argument, use the full name:

```{r q-syntax-10-setup}
`mean(1:10, na.rm = TRUE)` <- "Correct"
`mean(x = 1:10, , TRUE)` <- "Wrong"
`mean(, TRUE, x = c(1:10, NA))` <- "Wrong"
```

<p font-size:2em> Exercise : </p>
Fix following codes and run it with `Run code`. 
If it is correct, `Correct` will be returned.

```{r q-syntax-10, exercise = TRUE, exercise.setup = "q-syntax-10-setup"}
`mean(x = 1:10, , TRUE)`
`mean(, TRUE, x = c(1:10, NA))`
```

------

### Code blocks

`r emo::ji('pushpin')` Rules : 

- Curly braces, `{}`, define the most important hierarchy of R code. 
- To make this hierarchy easy to see:
- `{` should be the last character on the line. 
- Related code (e.g., an `if` clause, a function declaration, a trailing comma, …) must be on the same line as the opening brace.
- The contents should be indented by two spaces.
- `}` should be the first character on the line.

```R
# Good
if (y < 0 && debug) {
  message("y is negative")
}

if (y == 0) {
  if (x > 0) {
    log(x)
  } else {
    message("x is negative or zero")
  }
} else {
  y^x
}

# Bad
if (y < 0 && debug) {
message("Y is negative")
}

if (y == 0)
{
    if (x > 0) {
      log(x)
    } else {
  message("x is negative or zero")
    }
} else { y ^ x }
```

#### Inline statements

`r emo::ji('pushpin')` Rules : 

- It’s ok to drop the curly braces (`{ }`) for very simple statements that fit on one line, as long as they don’t have side-effects.

```R
# Good
y <- 10
x <- if (y < 20) "Too low" else "Too high"
```

- Function calls that affect control flow (like `return()`, `stop()` or `continue`) should always go in their own `{}` block:

```R
# Good
if (y < 0) {
  stop("Y is negative")
}

# Bad
if (y < 0) stop("Y is negative")
```

------

### Long lines

`r emo::ji('pushpin')` Rules : 

- Strive to limit your code to 80 characters per line. 
- This fits comfortably on a printed page with a reasonably sized font. 
- If you find yourself running out of room, this is a good indication that you should encapsulate some of the work in a separate function.
- If a function call is too long to fit on a single line, use one line each for the function name, each argument, and the closing `)`. 
- This makes the code easier to read and to change later.

```R

# Good
do_something_very_complicated(
  something = "that",
  requires = many,
  arguments = "some of which may be long"
)

# Bad
do_something_very_complicated("that", requires, many, arguments,
                              "some of which may be long"
                              )

```

- As described under Argument names, you can omit the argument names for very common arguments (i.e. for arguments that are used in almost every invocation of the function). 
- Short unnamed arguments can also go on the same line as the function name, even if the whole function call spans multiple lines.

<p font-size:2em> Question : </p>
```{r q-syntax-11, echo = FALSE}
question("Assume map function needs x, a, b, extra_argument_c, extra_argument_d. which can be allow to align with x in one-line?",
  answer("a", correct = FALSE),
  answer("b", correct = TRUE),
  answer("extra_argument_c", correct = FALSE),
  answer("extra_argument_d", correct = TRUE),
  allow_retry = TRUE,
  random_answer_order = TRUE,
  type = 'multiple'
)
```

- You may also place several arguments on the same line if they are closely related to each other. 
- For example, strings in calls to `paste()` or `stop()`. When building strings, where possible match one line of code to one line of output.

```R
# Good
paste0(
  "Requirement: ", requires, "\n",
  "Result: ", result, "\n"
)

# Bad
paste0(
  "Requirement: ", requires,
  "\n", "Result: ",
  result, "\n")
```

------

### Assignment

`r emo::ji('pushpin')` Rules : 

- Use `<-`, not `=`, for assignment.

```{r q-syntax-12-setup}
`x <- 5` <- "Correct"
`x = 5` <- "Wrong"
```

<p font-size:2em> Exercise : </p>
Fix following codes and run it with `Run code`. 
If it is correct, `Correct` will be returned.

```{r q-syntax-12, exercise = TRUE, exercise.setup = "q-syntax-12-setup"}
`x = 5`
```

------

### Semicolons

`r emo::ji('pushpin')` Rules : 

- Don’t put `;` at the end of a line, and don’t use `;` to put multiple commands on one line.

------

### Quotes

`r emo::ji('pushpin')` Rules : 

- Use `"`, not `'`, for quoting text. 
- The only exception is when the text already contains double quotes and no single quotes.

```{r q-syntax-13-setup}
`"Text"` <- "Correct"
`'Text'` <- "Wrong"
```

<p font-size:2em> Exercise : </p>
Fix following codes and run it with `Run code`. 
If it is correct, `Correct` will be returned.

```{r q-syntax-13, exercise = TRUE, exercise.setup = "q-syntax-12-setup"}
`'Text'`
```
